Freezing of a Weeks-Chandler-Anderson Fluid using classical Density Functional Theory

### 2020-11-10 papers/thesis-kirstie/thesis.tex
a couple edits in the abstract

\abstract{
  We use Classical Density Functional Theory (cDFT) to predict the 
  freezing of a Weeks-Chandler-Anderson (WCA) fluid. A WCA fluid 
  consists of soft spheres that exhibit the repulsive portion of the 
  Leonard-Jones potential widely used to model the interaction of two 
  neutral atoms. Our cDFT functional is constructed using Soft Fundamental 
  Theory (SFMT) with Tarazona's tensor expression for Phi3, and Schmidt's 
  erf model in which we have incorporated our temperature dependent 
  parameters to fit the results to those predicted by Monte-Carlo simulations. 
  Our functional was successful in predicting the freezing of the WCA fluid 
  with a fairly good match to Monte-Carlo simulations. This result suggests 
  that SFMT may provide a solid foundation for future density functionals 
  that will model real fluids.
}

>>>>

\abstract{
  We use Classical Density Functional Theory (cDFT) to predict the 
  freezing of a Weeks-Chandler-Anderson (WCA) fluid. A WCA fluid 
  consists of soft spheres that exhibit the repulsive portion of the 
  Leonard-Jones potential widely used to model the interaction of two 
  neutral atoms. Our cDFT functional is constructed using Soft Fundamental 
  Theory (SFMT) with Tarazona's tensor expression for $\Phi_3$, and Schmidt's
  erf model in which we have incorporated temperature dependent
  parameters to
  \davidsays{fit the results to those predicted by Monte-Carlo simulations}.
  Our functional was successful in predicting the freezing of the WCA fluid 
  with a fairly good match to Monte-Carlo simulations. This result suggests 
  that SFMT may provide a solid foundation for future density functionals 
  that will model real fluids.
}
